Galaxy Clustering Constraints on the Galaxy Size--Halo Connection

### 2017-08-31 paper/galsize_paper.tex
Slight expansion of beginning of results section

In \S~\ref{subsec:tests1} we show comparisons between the fiducial galaxy profile model described in \S~\ref{sec:model} and our SDSS sample. We demonstrate the sensitivity of galaxy clustering measurements to the post-infall evolution of satellite profiles in \S~\ref{subsec:tests2}, establishing the success of our fiducial model as non-trivial. In \S~\ref{subsec:tests3} we show that even highly idealized measurements of galaxy clustering and lensing are insensitive to assumptions about the relation between $\halospin$ and $\rhalf.$

>>>>

In \S~\ref{subsec:tests1} we show comparisons between the fiducial galaxy profile model described in \S~\ref{sec:model} and our SDSS sample. We demonstrate the sensitivity of galaxy clustering measurements to the post-infall evolution of satellite profiles in \S~\ref{subsec:tests2}, establishing the success of our fiducial model as non-trivial. In \S~\ref{subsec:tests3} we show that even highly idealized measurements of galaxy clustering and lensing are insensitive to assumptions about the relation between halo spin $\halospin$ and size $\rhalf$ of disk-dominated galaxies, implying that large-scale structure observations yield little-to-no constraining power on such assumptions.
